Ceph Parallel File System Evaluation Report

### 2013-08-19 ceph-eval.tex
Merge scott's patch for 7-11

Here, 0 is the default value of \verb!drop_cahces!; 1 is to free pagecaches, 2
is to free dentries and inodes, 3 is to free pagecache, dentries, and inodes.

@@

The full permutation of IOR parameters were not explored due to IO errors we encountered.
We were, however, able to record results in two extreme cases as far as
transfer size is concerned: 4 KB and 4 MB, using the same number of OSS servers
(4) and same block size (8 GB), the results are illustrated in Figure
\ref{fig:ior4k} and \ref{fig:ior4m}, we make the following observations:

@@

After the initial test results were found, various combinations of tweaks were
attempted including changing the number of filestore op threads, putting all
of the journals on the same disks as the data, doubling the OSD count, and
upgrading Ceph to a development version which reduces the seek overhead caused
by \texttt{pginfo} and \texttt{pglog} updates on XFS (These enhancements are
now included as of the Ceph Cuttlefish release).  The two biggest improvements
resulted from disabling CRC32c checksums and increasing the OSD count on the
server.  With these changes, we are seeing better results.

A script written by Inktank for internal Ceph testing was used to perform
parametric sweeps over Ceph configuration parameters to examine how different
tuning options affect performance on the DDN platform. The result of this
parameter probing is illustrated in Figure~\ref{fig:parametric}.

As a result of this testing, performance was again improved slightly by
increasing the size of various Ceph buffers and queues, enabling AIO journals,
and increasing the number of OSD op threads.

@@

Despite the excellent write throughput we saw during the individual server
tests, throughput did not scale.  A significant amount of time was spent
investigating this phenomenon. Ultimately, we were able to replicate this finding
when running concurrent disk throughput tests directly on the servers without
Ceph involved. The 2nd RAID processor on each DDN controller would max out when
3 or more LUNs were written concurrently. It turns out the root of the problem
was a regression on DDN firmware update -- in particular, the cache
mirroring was not behaving as it should.

@@

During these tests, a trend that previously had been seen became more apparent.
During reads, there were periods of high performance followed by periods of low
performance or outright stalls that could last for up to 20 seconds at a time. 
After several hours of diagnostics, Inktank observed that outstanding operations
on the clients were not being shown as outstanding on the OSDs.  This appeared
to be very similar to a problem Jim Schutt at Sandia National labs encountered
with TCP autotuning in the Linux Kernel.
\footnote{\url{http://marc.info/?l=ceph-devel&m=133009796706284&w=2}}.
TCP auto tuning enables TCP window scaling by default and automatically adjusts
the TCP receive window for each connection based on link conditions such as
bandwidth delay product. We have observed this will make a notable improvement
on Ceph read performance, as the results shown in
Figure~\ref{fig:rados-tcp-auto-disabled}.

@@

\begin{figure}[htb]
\centering
\includegraphics[width=5in]{rados-064-osd}
\caption{RADOS Bench Scaling on \# of OSD, Ceph 0.64, 4 MB IO, 8 Client Nodes}
\label{fig:rados-064-osd}
\end{figure}

@@

\begin{figure}[htb]
\centering
\includegraphics[width=5in]{rados-064-oss}
\caption{RADOS Bench Scaling on \# of Server, Ceph 0.64, 4 MB IO, 8 Client Nodes}
\label{fig:rados-064-oss}
\end{figure}

@@

ORNL installed kernel 3.9 on all of the test systems and Inktank performed a
RADOS Bench test to verify that there was no degradation vs previous tests.  The
results were extremely positive.

@@

@@

@@

In our particular setup, we have only one metadata server (MDS)
configured. Therefore, this is not a scalability test on the performance of
clustered MDS, which would be very interesting and might as well come later.
Instead, we focus on a single MDS, multiple clients (up to 8) and see how it
scales. The particular parameters we use for testing are:

@@

  \item Ceph performs \textbf{metadata + data} journaling, which is fine for host
  system that has locally attached disk. However, this presents a problem in DDN
  SFA10-like hardware, where the backend LUNs are exposed as block device
  through SRP over IB. The journaling write would requires double bandwidth
  compare to Lustre-like metadata only journaling mechanism. For Ceph to anything
  viable in this facility, there has to be a solution for this.

  \item Ceph is observed to have consistent results and linear scalability at the
  RADOS level. However, it broke down at the file system level with synthetic
  benchmark suites such as IOR. We have experienced large performance swings
  during different runs, very low read performance when transfer size is small,
  and IO errors tend to happen when system is under stress (more clients and
  large transfer sizes). These are not particularly reproducible results, but it
  suggests the level of maturity still have a long way to go.

>>>>

Here, 0 is the default value of \verb!drop_caches!; 1 is to free pagecaches, 2
is to free dentries and inodes, 3 is to free pagecache, dentries, and inodes.

@@

The full permutation of IOR parameters were not explored due to I/O errors we encountered.
We were, however, able to record results in two extreme cases as far as
transfer size is concerned: 4 KB and 4 MB, using the same number of OSS servers
(4) and same block size (8 GB), the results are illustrated in Figure
\ref{fig:ior4k} and \ref{fig:ior4m}, we make the following observations:

%% SCOTT - figures 4-7 do not seem to use a base of 0 for the Y axis. Is this common?
%% SCOTT - Can figures 6-7 have the same Y axis with either base 2 or base 10 values?

@@

After the initial test results, we tried various combinations of tweaks
including changing the number of filestore op threads, putting all
of the journals on the same disks as the data, doubling the OSD count, and
upgrading Ceph to a development version which reduces the seek overhead caused
by \texttt{pginfo} and \texttt{pglog} updates on XFS (these enhancements are
now included as of the Ceph Cuttlefish release).  The two biggest improvements
resulted from disabling CRC32c checksums and increasing the OSD count on the
server.  With these changes, we are seeing better results.

We ran a script written by Inktank for internal Ceph testing to perform
sweeps over Ceph configuration parameters to examine how different
tuning options affect performance on the DDN platform. The result of this
parameter probing is illustrated in Figure~\ref{fig:parametric}.

As a result of this testing, we improved performance slightly by
increasing the size of various Ceph buffers and queues, enabling AIO journals,
and increasing the number of OSD op threads.

@@

Despite the excellent write throughput we saw during the individual server
tests, throughput did not scale.  We spent a significant amount of time
investigating this phenomenon. Ultimately, we were able to replicate this finding
when running concurrent disk throughput tests directly on the servers without
Ceph involved. The second RAID processor on each DDN controller would max out when
three or more LUNs were written concurrently. It turns out the root of the problem
was a regression on DDN firmware update -- in particular, the cache
mirroring was not behaving as it should.

%% SCOTT - is running with cache mirroring off and option for a production system or not?
%% What are the consequences? Did DDN eventually provide a fix? If yes, were we able to test
%% with it or not?

@@

During these tests, a trend that previously had been seen became more apparent.
During reads, there were periods of high performance followed by periods of low
performance or outright stalls that could last for up to 20 seconds at a time.
After several hours of diagnostics, Inktank observed that outstanding operations
on the clients were not being shown as outstanding on the OSDs.  This appeared
to be very similar to a problem Jim Schutt at Sandia National labs encountered
with TCP autotuning in the Linux Kernel.\footnote{\url{http://marc.info/?l=ceph-devel&m=133009796706284&w=2}}
TCP auto tuning enables TCP window scaling by default and automatically adjusts
the TCP receive window for each connection based on link conditions such as
bandwidth delay product. We have observed this will make a notable improvement
on Ceph read performance, as the results shown in
Figure~\ref{fig:rados-tcp-auto-disabled}.

@@

%% SCOTT - the title in the figure needs to change IO to I/O

%% SCOTT - how do writes inc. journals exceed the client network max? Dual ports
%% on the single server?

\begin{figure}[htb]
\centering
\includegraphics[width=5in]{rados-064-osd}
\caption{RADOS Bench Scaling on \# of OSD, Ceph 0.64, 4 MB I/O, 8 Client Nodes}
\label{fig:rados-064-osd}
\end{figure}

@@

%% SCOTT - why does the client network max scale in figure 12 but not figure 11?
%% Do they no measure the same thing (i.e. a single server)? If not, the text
%% needs to make it more clear.

\begin{figure}[htb]
\centering
\includegraphics[width=5in]{rados-064-oss}
\caption{RADOS Bench Scaling on \# of Server, Ceph 0.64, 4 MB I/O, 8 Client Nodes}
\label{fig:rados-064-oss}
\end{figure}

@@

ORNL installed kernel 3.9 on all of the test systems and Inktank performed a
RADOS Bench test to verify that there was no degradation versus previous tests.  The
results were extremely positive.

@@

%% SCOTT - is figure 15 IOR over Ceph and 14 is RADOS bench? If so, can we
%% mention that 15 shows the filesystem performance?

@@

%% SCOTT - Can we use the same Y axis for these figures? Any comment from Inktank
%% as to why 4 KB performance is better than 4 MB performance?

@@

In our particular setup, we have only one metadata server (MDS)
configured. Therefore, this is not a scalability test on the performance of
clustered MDS, which would be very interesting.
Instead, we focus on a single MDS, multiple clients (up to 8) and see how it
scales. The particular parameters we use for testing are:

@@

  \item Ceph performs \textbf{metadata + data} journaling, which is fine for host
  system that has locally attached disk. However, this presents a problem in DDN
  SFA10-like hardware, where the backend LUNs are exposed as block device
  through SCSI Request Protocol (SRP) over IB. The journaling write requires twice the bandwidth
  compare to Lustre-like metadata-only journaling mechanism. For Ceph to be
  viable in this facility, we will need to address this.

  \item We observed consistent results and linear scalability at the
  RADOS level. However, we did not observe the same at the file system level with synthetic
  benchmark suites such as IOR. We have experienced large performance swings
  during different runs, very low read performance when transfer size is small,
  and I/O errors tend to happen when system is under stress (more clients and
  large transfer sizes). These are not particularly reproducible results, but it
  suggests that there are opporunities for code improvement and maturation.
